\chapter{Scope of Work}
\section{Scope of Work}
Active Directory, Microsoft Exchange Mail Server 2019 SE Implementation Work Scope:
\begin{itemize}
    \item Implement and Configure Hyper-V in all Physical Machines on DC and DR as per requirement.
    \item Install and configure Required Prerequisites.
    \item Create Virtual Machine for all Required Servers and install Windows Server with latest patch.
    \item In AD VMs, Configure pre-requisite of Active Directory.
    \item Installation of Active Directory Servers with integrated DNS.
    \item DNS configuration Forward and Reverse Zone.
    \item Organizational unit, Active Directory User and Security Group creation as per csv file provided by us to customer before start implementation.
    \item Group Policy configuration as per requirements.
    \item Installation of Mail Server two nodes per Datacenter with latest CU with Reverse Proxy and Witness.
    \item Database creation as per customer requirement.
    \item Configure Database Availability Group (DAG) and Configure Witness server.
    \item Configure High Availability of Mail Server and Database.
    \item Mail Server failover testing and performance check.
    \item Mailbox creation as per provided csv file from customer before start implementation.
    \item Distribution group creation as per document by customer before start implementation.
    \item Configure Mail server Virtual Directory and Implementation of SSL certificate.
    \item Internal Mail Flow Connector configure, and Internal Mail Flow Checking.
    \item Configure mail flow connector setting as per publishing requirement.
    \item Configure local DNS record and provide public DNS records to the customer for publishing.
    \item Configure and Publish Mail Server via Reverse Proxy Server and IronPort.
    \item Check Mail Flow internally and externally.
    \item Check mail connectivity of clients.
    \item AD, Mail Server, health checkup and performance monitoring.
    \item Testing, Monitoring, Performance checking and troubleshooting.
    \item Collect Required Resources for Deployment Procedure Document Delivery.
\end{itemize}
This scope covers the end-to-end deployment of a new Microsoft Exchange Server 2019 environment. It includes the installation, configuration, and integration of Exchange roles with existing infrastructure like Active Directory. Core tasks encompass mailbox database creation, send/receive connector setup, and client access services configuration. The final phase includes mail flow testing and the secure migration of user mailboxes from the legacy system. Post-implementation documentation and a handover to the operations team will complete the project
