I extend my deepest gratitude to my beloved mother, whose unwavering support and sacrifices have paved the way for us to embark on this remarkable journey. Having such incredible mother in my life is an immense honor and blessing. My aspiration is to lead a professional and personal life that fills them with pride. I indebted to Mohammad Shahidul Islam, PhD, my advisor and mentor. His infectious charisma and boundless energy leave an unforgettable impression, and I aspire to mirror his enthusiasm. His generous time, dedicated efforts, and insightful discussions throughout my degree are invaluable. I also express appreciation to all our Faculty Teachers for their invaluable guidance and constructive feedback.







My heartfelt thanks go to the Jahangirnagar University (IIT-JU) Administration for granting me an opportunity, enabling me to pursue my studies without any burden.
Finally, I want to acknowledge the unwavering support of all Class Friends, my Colleague and our Organization “Bank Asia PLC”. Encouragement and presence throughout my academic journey have been my greatest strength. To my parents, Friends, Colleague, and our Company’s unwavering support have been a source of inspiration during the most challenging times of my studies. presence has made this journey worthwhile. Thank you all for being my pillars of support.


Thank the other faculty members of IIT who have helped me directly or indirectly by providing their valuable support in completing this work.

I express my gratitude to all other sources from where I have found help. I indebted to those who have helped me directly or indirectly in completing this work.

Last but not least, I would like to thank all the staff of IIT, Jahangirnagar University and our friends who have helped me by giving their encouragement and cooperation throughout the work.